Mbh-n paper

### 2015-08-21 papers/mbhn/mbhn.tex
vaffanculo e venerdi

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}

@@

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

@@

%%A focal problem today in the dynamics of globular clusters is core collapse.
%%It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
%%observation has been less alert to the phenomenon. For many years the
%%central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.
%%Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a
%%limited photographic survey of ours \citep[Paper I]{djo84} found three more
%%cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and
%%\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been
%%remarked on \citep{can78}.
%%
%%As an example of how the new AASTeX object tagging macros work, we will
%%cite some of the ``Superlative'' objects mentioned in section 10 of
%%Trimble's (1992) review of astrophysics in the year 1991.  The youngest
%%star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
%%\object{70 Oph} was found to be the longest period spectroscopic binary.
%%The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
%%The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
%%while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
%%record for metal deficiency.  However, another low metallicitity
%%galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
%%largest redshift \object[PC 1247+3406]{source} in 1991 was found at
%%z=4.897.  Lastly, what paper would be complete without a mention of the
%%\object[M1]{Crab nebula}!

\section{Errors}

How do we compute the errors on the measured S\'ersic indices?
Montecarlo, bootstrapping or any other evil statistical method do not take into account the systematics,
which mainly depend on the decomposition model, i.e. the choice of the model components.
But we are lucky, since there are many other decompositions in the literature for our galaxies.
\cite{grahamdriver2007,laurikainen2010,sani2011,vika2012,beifiori2012,rusli2013,lasker2014data} have done this job.
So how about we do something similar to our first paper?
Let's say that I am not better than anybody else at decomposing galaxies 
(this is obviously absurd, given my incredible competence in vivisecting galaxies, but let's assume it for now).
I repeat the same game we did in our first paper.
For each galaxy, I take all the available measurements from the literature, including my own measurement,
and I compute the standard deviation of each set of measurements.
The standard deviation becomes the error of my own measurement.
When my measurement is the only available (nobody other than me ever decomposed that galaxy),
the errors is set to be equal to the median value of the distribution in Figure \ref{fig:hist} 
(almost the same we did in our first paper, see footnote 4).
Figure \ref{fig:hist}: here only galaxies with more than one measurement are contributing.
Take a galaxy, take its set of measurements (more than one!) of the S\'ersic index, 
compute the standard deviation of that set, the standard deviation becomes the error on my own measurement
(BTW, I am using the $n$ derived from the equivalent axis fit).
The distribution of the standard deviations is represented by the histogram.
The median value is $0.13$, which means a median uncertainty of $33\%$ on each individual measurement.
If we take of each set of measurements the average, then the error associated to the average 
and then the median value of all these errors, basically we are doing the same we did in footnote 4 of our first paper,
and the cool thing is that now we get the same number we got then ($20\%$).

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/histo_err_logn.eps}
\caption{}
\label{fig:hist}
\end{figure}

@@

Figure \ref{fig:mbhn}: Well, we now have the errors on each of OUR measurements of $n$.
We can plot bh mass vs $n$ (in log).

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_logn.eps}
\caption{}
\label{fig:mbhn}
\end{figure}

Figure \ref{fig:mbhavn}: Almost the same we did in our first paper. We take for each galaxy its set of measurements of $n$,
we reject measurements in disagreement for more than $50\%$,
we compute the median (not the average! this is different from what we did in the past, what do you think?) 
and the error associated to the mean, then we plot the black hole masses vs the median of log(n).
The correlation looks a bit steeper than in Figure \ref{fig:mbhn}, 
with less scatter. I bet you say it looks curved.

PS I will soon step back from the division bulges/ellipticals, 
I seriously believe there is no such division. 
I will explain this soon. ;)

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_median_logn.eps}
\caption{}
\label{fig:mbhavn}
\end{figure}

@@

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% All our observations were short direct exposures with CCD's.  We also have
%% a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
%% neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
%% via the links in the electronic edition.  Unfortunately this has nothing
%% whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500
%% chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
%% filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
%% $B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
%% filters, on the 1.5-m reflector. In the CTIO observations we tried to
%% concentrate on the shortest practicable wavelengths; but faintness, reddening,
%% and poor short-wavelength sensitivity often kept us from observing in $U$ or
%% even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
%% our field sizes were around 3 arcmin.
%%
%% The CCD images are unfortunately not always suitable, for very poor
%% clusters or for clusters with large cores.  Since the latter are easily
%% studied by other means, we augmented our own CCD profiles by collecting
%% from the literature a number of star-count profiles
%% \citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles
%% \citep{kin66,kin75} and electronographic profiles \citep{kro84}.
%% In a few cases we judged normality by eye estimates on one of the Sky
%% Surveys.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%%\section{Helicity Amplitudes}
%%
%%It has been realized that helicity amplitudes provide a convenient means
%%for Feynman diagram\footnote{Footnotes can be inserted like this.}
%%evaluations.  These amplitude-level techniques
%%are particularly convenient for calculations involving many Feynman
%%diagrams, where the usual trace techniques for the amplitude
%%squared becomes unwieldy.  Our calculations use the helicity techniques
%%developed by other authors \cite[]{hag86}; we briefly summarize below.
%%
%%\subsection{Formalism} \label{bozomath}
%%
%%%% The equation environment wil produce a numbered display equation.
%%
%%A tree-level amplitude in $e^+e^-$ collisions can be expressed in
%%terms of fermion strings of the form
%%\begin{equation}
%%\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
%%\hat a_nu(p_1,\sigma_1) ,
%%\end{equation}
%%where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
%%and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
%%and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
%%operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
%%four-momenta, gauge-boson polarization vectors or fermion strings with
%%an uncontracted Lorentz index associated with final-state fermions.
%%
%%%% The \notetoeditor{TEXT} command allows the author to communicate
%%%% information to the copy editor.  This information will appear as a
%%%% footnote on the printed copy for the manuscript style file.  Nothing will
%%%% appear on the printed copy if the preprint or
%%%% preprint2 style files are used.
%%
%%%% The eqnarray environment produces multi-line display math. The end of
%%%% each line is marked with a \\. Lines will be numbered unless the \\
%%%% is preceded by a \nonumber command.
%%%% Alignment points are marked by ampersands (&). There should be two
%%%% ampersands (&) per line.
%%
%%In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
%%print} representation the $\gamma$ matrices are expressed
%%in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
%%\begin{eqnarray}
%%\gamma^\mu  & = &
%% \left(
%%\begin{array}{cc}
%%0 & \sigma^\mu_+ \\
%%\sigma^\mu_- & 0
%%\end{array}	  \right) ,
%% \gamma^5= \left(
%%\begin{array}{cc}
%%-1 &   0\\
%%0 &	1
%%\end{array}	  \right)  , \nonumber \\
%%\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
%%\end{eqnarray}
%%giving
%%\begin{equation}
%%\hat a= \left(
%%\begin{array}{cc}
%%0 & (\hat a)_+\\
%%(\hat a)_- & 0
%%\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
%%\end{equation}
%%The spinors are expressed in terms of two-component Weyl spinors as
%%\begin{equation}
%%u=\left(
%%\begin{array}{c}
%%(u)_-\\
%%(u)_+
%%\end{array}\right), v={\bf (}\vdag_+{\bf ,}	\vdag_-{\bf )} .
%%\end{equation}
%%
%%%% Putting eqnarrays or equations inside the mathletters environment groups
%%%% the enclosed equations by letter. For instance, the eqnarray below, instead
%%%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%%%% LaTeX the paper and look at the output to see the results.
%%
%%The Weyl spinors are given in terms of helicity eigenstates
%%$\chi_\lambda(p)$ with $\lambda=\pm1$ by
%%\begin{mathletters}
%%\begin{eqnarray}
%%u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
%%v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
%%_{-\lambda}(p)
%%\end{eqnarray}
%%\end{mathletters}
%%
%%%% This section contains more display math examples, including unnumbered
%%%% equations (displaymath environment). The last paragraph includes some
%%%% examples of in-line math featuring a couple of the AASTeX symbol macros.
%%
%%\section{Floating material and so forth}
%%
%%%% The displaymath environment will produce the same sort of equation as
%%%% the equation environment, except that the equation will not be numbered
%%%% by LaTeX.
%%
%%Consider a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{displaymath}
%%d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{displaymath}
%%d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{displaymath}
%%x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
%%\end{displaymath}
%%\begin{displaymath}
%%y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{displaymath}
%%
%%In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
%%angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
%%It is not clear how these sorts of analyses may affect determination of
%% $M_{\sun}$, but the assumption is that the alternate results
%%should be less than 90\degr\ out of phase with previous values.
%%We have no observations of \ion{Ca}{2}.
%%Roughly \slantfrac{4}{5} of the electronically submitted abstracts
%%for AAS meetings are error-free.
%%
%%%% If you wish to include an acknowledgments section in your paper,
%%%% separate it off from the body of the text using the \acknowledgments
%%%% command.
%%
%%%% Included in this acknowledgments section are examples of the
%%%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%%%% argument when you want to print the url directly in the text. Otherwise,
%%%% use either \url or \anchor, with the HREF as the first argument and the
%%%% text to be printed in the second.
%%
\acknowledgments
%chien peng, peter erwin
%%
%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
%%doing the math in section~\ref{bozomath}.
%%More information on the AASTeX macros package is available \\ at
%%\url{http://www.aas.org/publications/aastex}.
%%For technical support, please write to
%%\email{aastex-help@aas.org}.
%%
%%%% To help institutions obtain information on the effectiveness of their
%%%% telescopes, the AAS Journals has created a group of keywords for telescope
%%%% facilities. A common set of keywords will make these types of searches
%%%% significantly easier and more accurate. In addition, they will also be
%%%% useful in linking papers together which utilize the same telescopes
%%%% within the framework of the National Virtual Observatory.
%%%% See the AASTeX Web site at http://aastex.aas.org/
%%%% for information on obtaining the facility keywords.
%%
%%%% After the acknowledgments section, use the following syntax and the
%%%% \facility{} macro to list the keywords of facilities used in the research
%%%% for the paper.  Each keyword will be checked against the master list during
%%%% copy editing.  Individual instruments or configurations can be provided 
%%%% in parentheses, after the keyword, but they will not be verified.
%%
%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
%%
%%%% Appendix material should be preceded with a single \appendix command.
%%%% There should be a \section command for each appendix. Mark appendix
%%%% subsections with the same markup you use in the main body of the paper.
%%
%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%%%% The equation counter will reset when it encounters the \appendix
%%%% command and will number appendix equations (A1), (A2), etc.
%%
%%\appendix
%%
%%\section{Appendix material}
%%
%%Consider once again a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{mathletters}
%%\begin{displaymath}
%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{equation}
%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{equation}
%%\begin{eqnarray}
%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{eqnarray}
%%\end{mathletters}
%%
%%For completeness, here is one last equation.
%%\begin{equation}
%%e = mc^2
%%\end{equation}

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}

%%\begin{thebibliography}{}
%%\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
%%    109, 301
%%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
%%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
%%    McClintock, J. E.  1978, \apj, 224, 39
%%\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
%%    \& King, I. R.  1984, \apjl, 277, L49
%%\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
%%    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
%%\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
%%    \& van den Bergh, S.  1984, \aj, 89, 1816
%%\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
%%\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
%%\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
%%\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
%%\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
%%    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
%%\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
%%    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
%%\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
%%    \& Wasserman, L. H.  1984, \pasp, 96, 198
%%\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
%%    \& Wood, R.  1968, \mnras, 138, 495
%%\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
%%    \& O'Neil, E. J.  1978, \apjs, 37, 27
%%\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
%%    \& Sandage, A.  1985, \aj, 90, 473
%%\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
%%\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
%%\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
%%    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
%%\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
%%\end{thebibliography}

@@

%%
%% End of file `sample.tex'.

>>>>

\usepackage{natbib}
%\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}

@@

@@

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]

Elliptical (30)	       & BCES $(Y|X)$		    & $-25.46 \pm 1.12$ & $38.47 \pm 114.45$ & $0.76$ & $-$ & $6.37$ \\
		       & mFITEXY $(Y|X)$	    & $-25.74 \pm 0.18$ & $-9.74 \pm 1.59$ & $0.76$ & $0.24^{+0.32}_{-0.24}$ & $0.94$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-25.65 \pm 0.21$ & $-7.87 \pm 2.15$ & $0.76$ & $0.61 \pm 0.22$ & $1.06$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-25.46 \pm 0.23$ & $-10.73 \pm 3.21$ & $0.76$ & $-$ & $1.29$ \\
		       & mFITEXY $(X|Y)$	    & $-25.74 \pm 0.20$ & $-10.42 \pm 1.79$ & $0.76$ & $0.22^{+0.38}_{-0.22}$ & $1.29$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-25.72 \pm 0.28$ & $-10.92 \pm 2.70$ & $0.76$ & $0.73 \pm 0.34$ & $1.33$ \\ [0.5em]
		       & BCES Bisector  	    & $-25.46 \pm 0.20$ & $0.03 \pm 0.05$ & $0.76$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-25.74 \pm 0.19$ & $-10.07 \pm 1.19$ & $0.76$ & $-$ & $1.26$ \\
		       & {\tt linmix\_err} Bisector & $-25.68 \pm 0.25$ & $-9.15 \pm 1.74$ & $0.76$ & $-$ & $1.16$ \\ [0.5em]

Lenticular (11)	       & BCES $(Y|X)$		    & $-22.08 \pm 1.66$ & $33.52 \pm 98.87$ & $0.33$ & $-$ & $6.09$ \\
		       & mFITEXY $(Y|X)$	    & $-22.11 \pm 0.24$ & $-6.31 \pm 2.45$ & $0.33$ & $0.42^{+0.28}_{-0.17}$ & $0.71$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.08 \pm 0.19$ & $-6.83 \pm 1.16$ & $0.33$ & $-$ & $0.71$ \\
		       & mFITEXY $(X|Y)$	    & $-21.94 \pm 0.44$ & $-13.16 \pm 7.91$ & $0.33$ & $0.61^{+0.60}_{-0.56}$ & $1.39$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.08 \pm 0.30$ & $0.06 \pm 0.05$ & $0.33$ & $-$ & $1.09$ \\
		       & mFITEXY Bisector	    & $-22.05 \pm 0.35$ & $-8.55 \pm 2.79$ & $0.33$ & $-$ & $0.84$ \\
		       & {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]

Spiral (17)	       & BCES $(Y|X)$		    & $-22.33 \pm 0.26$ & $-5.31 \pm 5.83$ & $0.18$ & $-$ & $1.15$ \\
		       & mFITEXY $(Y|X)$	    & $-22.22 \pm 0.19$ & $-2.17 \pm 0.98$ & $0.18$ & $0.53^{+0.24}_{-0.13}$ & $0.72$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.26 \pm 0.24$ & $-1.53 \pm 1.88$ & $0.18$ & $0.71 \pm      0.22$ & $0.78$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.33 \pm 0.26$ & $-5.19 \pm 3.77$ & $0.18$ & $-$ & $1.13$ \\
		       & mFITEXY $(X|Y)$	    & $-22.28 \pm 0.44$ & $-9.08 \pm 5.31$ & $0.51$ & $1.12^{+0.54}_{-0.31}$ & $1.83$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.24 \pm 0.71$ & $-11.12 \pm 13.59$ & $0.18$ & $1.95 \pm 2.47$ & $2.24$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.33 \pm 0.26$ & $-5.25 \pm 3.38$ & $0.18$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-22.23 \pm 0.33$ & $-3.60 \pm 1.29$ & $0.18$ & $-$ & $0.92$ \\
		       & {\tt linmix\_err} Bisector & $-22.25 \pm 0.53$ & $-2.88 \pm 2.66$ & $0.18$ & $-$ & $0.84$ \\ [0.5em]

\tableline 
\tableline
\end{tabular}
\end{table*}

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
Early-type (43)	       & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-24.70 \pm 0.17$ & $-8.28 \pm 0.87$ & $0.64$ & $0.58 \pm 0.17$ & $0.98$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-24.55 \pm 0.14$ & $-8.25 \pm 0.63$ & $0.64$ & $-$ & $0.96$ \\
		       & mFITEXY $(X|Y)$	    & $-24.74 \pm 0.14$ & $-9.13 \pm 0.68$ & $0.64$ & $0.23^{+0.25}_{-0.23}$ & $1.08$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-24.73 \pm 0.18$ & $-9.08 \pm 0.87$ & $0.64$ & $0.60 \pm 0.21$ & $1.07$ \\ [0.5em]
		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]

Bulges (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.20 \pm 0.17$ & $-2.48 \pm 1.21$ & $0.26$ & $0.67 \pm 0.15$ & $0.83$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.25 \pm 0.20$ & $-5.85 \pm 1.83$ & $0.26$ & $-$ & $1.15$ \\
		       & mFITEXY $(X|Y)$	    & $-22.17 \pm 0.25$ & $-7.65 \pm 2.43$ & $0.26$ & $0.87^{+0.30}_{-0.18}$ & $1.46$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.16 \pm 0.31$ & $-7.80 \pm 3.89$ & $0.26$ & $1.18 \pm 0.65$ & $1.48$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.25 \pm 0.20$ & $-5.87 \pm 2.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [0.5em]

%All (xx)		& BCES $(Y|X)$  	     & $$ & $$ & $$ & $$ & $$ \\
%			& mFITEXY $(Y|X)$	     & $$ & $$ & $$ & $$ & $$ \\
%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
%			& BCES $(X|Y)$  	     & $$ & $$ & $$ & $$ & $$ \\
%			& mFITEXY $(X|Y)$	     & $$ & $$ & $$ & $$ & $$ \\
%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
%			& BCES Bisector 	     & $$ & $$ & $$ & $$ & $$ \\
%			& mFITEXY Bisector	     & $$ & $$ & $$ & $$ & $$ \\
%			& {\tt linmix\_err} Bisector & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
%

\tableline 
\tableline
\end{tabular}
\label{tab:lregsph} 
\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
\end{table*}

@@

%%
\acknowledgments

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}

@@
